An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-13 aistats2017.tex
fix to empiricial c_\theta,\theta' value and clarified why we use gamma = 2

\begin{table}[t]
    \caption{Error ($L_\infty$) in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$}
    \label{tab:xcorr}
    \centering
    \begin{tabular}{l l l l}
    ${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
    \hline
    4000 & 0.9 & 1 & 1.0e-4  \\
    4000 & 0.8 & 0.03 & 5.0e-6 \\
    \end{tabular}
\end{table}

@@

We next test logistic regression for the binary classification of 1s
versus 7s on a subset of the MNIST8M dataset, a larger version of
MNIST~\citep{lecun-mnisthandwrittendigit-2010}. We randomly subsampled
450k training and 192k testing points.
%%% The pixels are scaled in $[0,1]$  - JFC Why ????
We impose a uniform prior on $\theta$ and again use a random walk
proposer, this time with covariance matrix $0.05I$. The temperature is
set at $T=1000$. We run the three tests for 3000 samples and again use 100
as the starting minibatch size. Method~\citet{cutting_mh_2014} used
per-test error of $\epsilon=0.05$.  For~\citet{icml2014c1_bardenet14},
we used $\gamma=2.0$ (discounting factor). We tried to use the
symbolic bound for $C_{\theta,\theta'}$ for Logistic regression
from~\citet{icml2014c1_bardenet14}, but found it to be too high. Instead we use
the empirical $C_{\theta,\theta'}$ from the entire dataset without including the
test for this test, so again our results represent a lower bound for this
method.

>>>>

\begin{table}[t]
    \caption{Error ($L_\infty$) in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$}
    \label{tab:xcorr}
    \centering
    \begin{tabular}{l l l l}
    ${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
    \hline
    4000 & 0.9 & 1 & 1.0e-4  \\
    4000 & 0.8 & 0.03 & 5.0e-6
    \end{tabular}
\end{table}

@@

We next test logistic regression for the binary classification of 1s
versus 7s on a subset of the MNIST8M dataset, a larger version of
MNIST~\citep{lecun-mnisthandwrittendigit-2010}. We randomly subsampled
450k training and 192k testing points.
%%% The pixels are scaled in $[0,1]$  - JFC Why ????
We impose a uniform prior on $\theta$ and again use a random walk
proposer, this time with covariance matrix $0.05I$. The temperature is
set at $T=1000$. We run the three tests for 3000 samples and again use 100
as the starting minibatch size. Method~\citet{cutting_mh_2014} used
per-test error of $\epsilon=0.05$.  For~\citet{icml2014c1_bardenet14},
we use their recommended discounting factor value of $\gamma=2.0$. We tried to use the
symbolic bound for $C_{\theta,\theta'}$ for Logistic regression
from~\citet{icml2014c1_bardenet14}, but found it to be too high. Instead we use
the empirical $C_{\theta,\theta'}$ from the entire dataset and do not add its
computation time when considering runtime, so again our results represent a
lower bound for this method.
